---
title: "Random6"
author: "Alex Abos"
date: "2/21/2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
# Load packages
library('ggplot2') # visualization
library('ggthemes') # visualization
library('scales') # visualization
library('dplyr') # data manipulation
library('mice') # imputation
library('randomForest') # classification algorithm
library('zoo')
library('sjPlot')
library('Hmisc')
library('xgboost')
library('reshape')
library('data.table')
library('lubridate')
```


## Random6 Project

Let's start with the competition! Both train and test datasets are txt file with | separator. 

```{train, echo=FALSE}
setwd('data')
train=read.table("train.txt",sep="|",header=TRUE)

data_train <- as.data.table(read.table(paste0(getwd(),'/data/train2.txt'), header = T, sep = '|', stringsAsFactors = F))

data_test <- as.data.table(read.table(paste0(getwd(),'/data/test2.txt'), header = T, sep = '|', stringsAsFactors = F))

```

```{r, echo=FALSE}
str(train)
```

Dimensions are 3351017 x 8
Colum names: 
"ID_Customer" = Identificador de cliente  
"Cod_Prod" = C처digo de la modalidad de producto contratado      
"Cod_Fecha" = Fecha de contrataci처n de la modalidad de producto   
"Socio_Demo_01" = Edad
"Socio_Demo_02" = Antig체edad
"Socio_Demo_03" = Ingresos
"Socio_Demo_04" = Sexo (1: Hombre, 2: Mujer)
"Socio_Demo_05" = Segmento (00: Particular | 01:Agricultor | 02:Comercio | 03:Aut처nomo)

## Fixing Formats

All variables are int except the Cod_Fecha

```{r, echo=FALSE}
train$Cod_Fecha<-as.Date(as.yearmon(train$Cod_Fecha))
```

## Inspecting variables

```{r}
# Use ggplot2 to visualize the relationship 
ggplot(train, aes(x = Socio_Demo_03, fill = factor(Socio_Demo_04))) +
  geom_bar(stat='count', position='dodge') +
  scale_x_continuous(breaks=c(1:11)) +
  labs(x = 'Ingresos') +
  theme_few()
```

```{r}
sjp.grpfrq(train$Socio_Demo_03, train$Socio_Demo_04)
```

```{r}
ggplot(data=train,aes(x=Socio_Demo_01)) + 
  geom_bar(alpha=0.75,fill="tomato",color="black") +
  ggtitle("Age Distribution") 
```



Are there any missing values?
```{r}
sapply(train,function(x)any(is.na(x)))
```

No missing values :)

Fer proves per pivotar

```{r}
train2<-train[1:50,]
```

```{r}
train3<-cast(train2, Cod_Prod ~ ID_Customer)
train4<-train3[,2:12] 
a4<-a[,2:12]
train4[a4]<-1
train3[,2:12]<-train4
```

